Model to study co-evolution of trade an culture

### 2015-02-24 article.tex
fix bib stuff

\section{Introduction}
In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire. Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi_trade_1957}). Following \cite{epstein_growing_1996,
lake_trends_2014,
kohler_dynamics_2000,
tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.

@@

Later it could be used to study other model such as those developed by 
\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,
polanyi_livelihood_1977} about the early economical mechanisms.

>>>>

\section{Introduction}
In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire. Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi_trade_1957}). Following \cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.

@@

Later it could be used to study other model such as those developed by 
\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,polanyi_livelihood_1977} about the early economical mechanisms.
